biclaR: Estimating the socio-environmental impacts of car substitution by bicycle and public transit using open tools

### 2023-10-11 paper/PaperTRA/PaperTRA.Rmd
minor changes and knit

To estimate the car emissions, we used the EMEP/EEA's COPERT software v5 methods and reference values [@COPERT] for a Tier 3 detail level. 
We used a family-size vehicle, EURO standard, and gasoline or diesel fuel.
All trips were considered to be made under urban conditions and at an average speed of 15 km/h during rush hour periods.
Since the average distance traveled per trip influences the overconsumption and emissions from cold-start engine operation, we estimated energy and emission factors for different ranges of trips at 500-meter intervals.
In addition, we assumed an occupancy rate of 1.61 passengers *per* car [@IMOB].

Regarding the PT, we considered the emission factor values reported in the environmental and sustainability reports of the PT operators in the LMA [@Carris2019s; @Metro2019s; @CP2019s; @Transtejo2014].

Emissions were estimated for the following atmospheric pollutants: CO, PM10, NOx, and VOC; and for the main green house gases: CO~2, CH~4, and N~2~O, converted in CO~2~eq.
In particular, for the urban train and tram -- with 100% electric traction -- only CO~2~eq emissions were considered (resulting from the production of electricity, considering a "well-to-tank" approach), since the other pollutants are not emitted locally.

@@

Our findings suggest that a bicycle and PT combination could viably replace 20% of current LMA trips, with an additional 12% of PT journeys prone to further substitution. 
<!-- repeated? not correct -->

>>>>

To estimate the car emissions, we used the EMEP/EEA's COPERT software v5 methods and reference values [@COPERT] for a Tier 3 detail level. 
We used a family-size vehicle, EURO standard, and gasoline or diesel fuel.
All trips were considered to be made under urban conditions and at an average speed of 15 km/h during rush hour periods.
Since the average distance traveled per trip influences the overconsumption and emissions from cold-start engine operation, we estimated energy and emission factors for different ranges of trips at 500-meter intervals.
In addition, we assumed an occupancy rate of 1.6 passengers *per* car [@IMOB].

Regarding PT, we considered the emission factor values reported in the environmental and sustainability reports of the PT operators in the LMA [@Carris2019s; @Metro2019s; @CP2019s; @Transtejo2014].

Emissions were estimated for the following atmospheric pollutants: CO, PM10, NOx, and VOC; and for the main green house gases: CO~2~, CH~4~, and N~2~O, converted in CO~2~eq.
In particular, for the urban train and tram -- with 100% electric traction -- only CO~2~eq emissions were considered (resulting from the production of electricity, considering a "well-to-tank" approach), since the other pollutants are not emitted locally.

@@

Our findings suggest that cycling and PT *in combination* could viably replace 10% of current LMA trips, with an additional 6% of PT journeys prone to further substitution. 
<!-- repeated? not correct -->

### 2023-10-11 paper/PaperTRA/PaperTRA.tex
minor changes and knit

To estimate the car emissions, we used the EMEP/EEA's COPERT software v5
methods and reference values {[}13{]} for a Tier 3 detail level. We used
a family-size vehicle, EURO standard, and gasoline or diesel fuel. All
trips were considered to be made under urban conditions and at an
average speed of 15 km/h during rush hour periods. Since the average
distance traveled per trip influences the overconsumption and emissions
from cold-start engine operation, we estimated energy and emission
factors for different ranges of trips at 500-meter intervals. In
addition, we assumed an occupancy rate of 1.61 passengers \emph{per} car
{[}3{]}.

Regarding the PT, we considered the emission factor values reported in
the environmental and sustainability reports of the PT operators in the
LMA {[}14--17{]}.

Emissions were estimated for the following atmospheric pollutants:
CO\textsubscript{2}eq, CO, PM10, NOx, and VOC. In particular, for the
urban train and tram -- with 100\% electric traction -- only
CO\textsubscript{2}eq emissions were considered (resulting from the
production of electricity, considering a ``well-to-tank'' approach),
since the other pollutants are not emitted locally.

@@

\caption{\label{tab:summary1}\label{summary1}Summary of the cycling potencial of intermodality scenario.}
\centering
\begin{tabular}[t]{llr>{\raggedleft\arraybackslash}p{6em}>{\raggedleft\arraybackslash}p{6em}>{\raggedleft\arraybackslash}p{6em}>{\raggedleft\arraybackslash}p{6em}}
\toprule
Target & Routing & Total trips & Baseline Cycling + PT & Potencial Cycling + PT & Avoided CO2eq (ton/yr) & SE Benefits for 10 years (thousand €)\\
\midrule
4\% & safe & 538 514 & 2 312 & 20 385 & 5 920 & 230 270\\
4\% & direct & 500 880 & 2 274 & 18 944 & 6 011 & 223 720\\
10\% & safe & 538 514 & 2 312 & 52 324 & 15 192 & 591 790\\
10\% & direct & 500 880 & 2 274 & 48 609 & 15 414 & 574 200\\
\bottomrule
\end{tabular}
\end{table}

@@

Our findings suggest that a bicycle and PT combination could viably
replace 20\% of current LMA trips, with an additional 12\% of PT
journeys prone to further substitution.

>>>>

To estimate the car emissions, we used the EMEP/EEA's COPERT software v5
methods and reference values {[}13{]} for a Tier 3 detail level. We used
a family-size vehicle, EURO standard, and gasoline or diesel fuel. All
trips were considered to be made under urban conditions and at an
average speed of 15 km/h during rush hour periods. Since the average
distance traveled per trip influences the overconsumption and emissions
from cold-start engine operation, we estimated energy and emission
factors for different ranges of trips at 500-meter intervals. In
addition, we assumed an occupancy rate of 1.6 passengers \emph{per} car
{[}3{]}.

Regarding PT, we considered the emission factor values reported in the
environmental and sustainability reports of the PT operators in the LMA
{[}14--17{]}.

Emissions were estimated for the following atmospheric pollutants: CO,
PM10, NOx, and VOC; and for the main green house gases:
CO\textsubscript{2}, CH\textsubscript{4}, and N\textsubscript{2}O,
converted in CO\textsubscript{2}eq. In particular, for the urban train
and tram -- with 100\% electric traction -- only CO\textsubscript{2}eq
emissions were considered (resulting from the production of electricity,
considering a ``well-to-tank'' approach), since the other pollutants are
not emitted locally.

@@

\caption{\label{tab:summary1}\label{summary1}Summary of the cycling potencial of intermodality scenario and its socio-environmental benefits for the cycling legs.}
\centering
\begin{tabular}[t]{llr>{\raggedleft\arraybackslash}p{6em}>{\raggedleft\arraybackslash}p{6em}>{\raggedleft\arraybackslash}p{6em}>{\raggedleft\arraybackslash}p{6em}}
\toprule
Target & Routing & Total trips & Baseline Cycling + PT & Potencial Cycling + PT & Avoided CO2eq (ton/yr) & SE Benefits for 10 years (thousand €)\\
\midrule
4\% & safe & 538 514 & 2 312 & 20 385 & 5 920 & 230 270\\
4\% & direct & 500 880 & 2 274 & 18 944 & 6 011 & 223 720\\
10\% & safe & 538 514 & 2 312 & 52 324 & 15 192 & 591 790\\
10\% & direct & 500 880 & 2 274 & 48 609 & 15 414 & 574 200\\
\bottomrule
\end{tabular}
\end{table}

@@

Our findings suggest that cycling and PT \emph{in combination} could
viably replace 10\% of current LMA trips, with an additional 6\% of PT
journeys prone to further substitution.
